### Vignette: Using ExcelToShiny

---
title: "Using ExcelToShiny"
author: "Lily Clements"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using ExcelToShiny}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, eval = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, eval = FALSE}
library(ggplot2)
library(ExcelToShiny)
library(readxl)
library(dplyr)
library(rio)
library(NHANES)
library(shiny)
library(shinydashboard)
```

# Introduction
This vignette demonstrates how to use the `ExcelToShiny` package to create a Shiny dashboard from an Excel spreadsheet.

## Loading an Excel Spreadsheet
To demonstrate the usage of `build_shiny`, we'll first load an example Excel file.

```{r load-data, message=FALSE, warning=FALSE, eval = FALSE}
# Path to the example Excel file
example_excel <- rio::import_list("data/nhanes_data.xlsx")
```

## Preparing the Data

We'll prepare the `NHANES` dataset by selecting individual records and ensuring that the `ID` column is in character format.

```{r prepare-data, message=FALSE, warning=FALSE, eval = FALSE}
# Load the NHANES dataset
data(NHANES)

# Prepare the data by selecting individual records
NHANES_by_ind <- NHANES %>%
  group_by(ID) %>%
  mutate(count = 1:n()) %>%
  filter(count == 1) %>%
  ungroup()

# Ensure that the ID column is in character format
NHANES_by_ind$ID <- as.character(NHANES_by_ind$ID)
```

## Loading Credentials

We'll load the credentials required for the Shiny app. This isn't always needed - but in our example, we use this in the "Download" tab.

```{r load-credentials, message=FALSE, warning=FALSE, eval = FALSE}
# Source the credentials data
source("data/credentials_data.R")
```

## Creating a Shiny Dashboard

Now, we will use the `build_shiny` function to create a Shiny dashboard based on the loaded Excel file and prepared data.

```{r create-dashboard, message=FALSE, warning=FALSE, eval = FALSE}
# Create the Shiny dashboard using the Excel file and prepared data
build_shiny(title = "Testing Shiny Dashboard",
            data_list = example_excel,
            data_frame = NHANES_by_ind,
            status = "primary",
            colour = "blue",
            key_var = "ID")
```

The `build_shiny()` function generates a Shiny app.

# Conclusion

This vignette has shown how to use the `ExcelToShiny` package to generate a Shiny dashboard from an Excel spreadsheet and a prepared dataset. 

There is documentation on the different elements of the Excel Spreadsheet available. 